% (The MIT License)
%
% Copyright (c) 2023 Yegor Bugayenko
%
% Permission is hereby granted, free of charge, to any person obtaining a copy
% of this software and associated documentation files (the 'Software'), to deal
% in the Software without restriction, including without limitation the rights
% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
% copies of the Software, and to permit persons to whom the Software is
% furnished to do so, subject to the following conditions:
%
% The above copyright notice and this permission notice shall be included in all
% copies or substantial portions of the Software.
%
% THE SOFTWARE IS PROVIDED 'AS IS', WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
% SOFTWARE.

\documentclass{article}
\usepackage{../pmba}
\newcommand*\thetitle{Resources Management}
\begin{document}

\plush{\pmbaTitlePage{6}}

\pmbaQuestion
  {One of your programmers is lacking behind: \emph{no contribution} from him for more than three months. Who should be fired?}
  {Him}
  {You}
  {Both}
  {Nobody}
  {responsibility}

\pmbaQuestion
  {You want better \emph{engagement} of your team into the project, what is your best instrument for that?}
  {Fun}
  {Challenges}
  {Appreciation}
  {Money}
  {pyramid}

\pmbaQuestion
  {Two programmers argue. Your job, as a project manager, is to ...}
  {Silence them down}
  {Find a compromise}
  {Take one side}
  {Encourage the fight}
  {conflict}

\pmbaQuestion
  {A programmer says that she failed her task because her cat was sick --- she had to spend the entire day in the hospital. ``Will you \emph{punish} me?'' she asks. What do you answer?}
  {``Let's ask the team to decide.''}
  {``Of course, not! You have a reasonable excuse.''}
  {``This time I won't, but next time be more responsible!''}
  {``Why do you ask me?''}
  {slavery}

\pmbaQuestion
  {A programmer asks for a raise, motivating it by the fact that he has built the entire payment module and now only he can maintain it. What do you do?}
  {Fire him}
  {Give him and everybody a small raise}
  {Promise him a raise}
  {Give him a raise, and a bonus}
  {silo, turnover}

\pmbaQuestion
  {You join a team where morale is low: people quit, no enthusiasm, gossips, etc. What would be your primary focus?}
  {Organizing team building sessions}
  {Sorting out the backlog}
  {Hiring refreshment}
  {Firing mood breakers}
  {morale}

\pmbaQuestion
  {A good programmer that you can't lose comes to you with a 2x job offer from Company X, asking for a raise. What do you do?}
  {Let him go}
  {Negotiate, pay 1.5x}
  {Try to bully Company X to make them call off the offer}
  {Give him a raise}
  {fire}

\pmbaQuestion
  {You notice that a programmer is watching YouTube while the deadline is approaching. You...}
  {Fire him}
  {Ask him ``What are you doing?''}
  {Talk to him later}
  {Join him}
  {micromanagement}

\plush{
  \pptBanner{Homework:}
  Design a ``\emph{Job Offer}'' for a new programmer that might join your team.
  Explain their how your team will reward and punish him/her for good and bad performance.
}

\plush{
  \pptBanner{Read this:}
  \href{https://www.yegor256.com/2019/06/19/how-much-they-suffer.html}{How Much Do They Suffer?} (2019)\par
  \href{https://www.yegor256.com/2019/01/22/10x-paychecks.html}{10x Paychecks for 10x Programmers} (2019)\par
  \href{https://www.yegor256.com/2017/06/06/gluten-free-management.html}{Gluten-Free Management Recipes} (2017)\par
  \href{https://www.yegor256.com/2017/01/03/how-much-you-love-conflicts.html}{How Much Do You Love Conflict?} (2017)\par
  \href{https://www.yegor256.com/2016/06/21/how-to-hire-programmer.html}{How to Hire a Programmer} (2016)\par
  \href{https://www.yegor256.com/2016/01/05/how-to-punish-employees.html}{How Do You Punish Your Employees?} (2016)\par
  \href{https://www.yegor256.com/2015/12/29/turnover-is-good-for-maintainability.html}{Employee Turnover Is Good for the Maintainability of Your Code Base} (2015)\par
  \href{https://www.yegor256.com/2015/09/22/micromanagement.html}{Are You a Micromanager?} (2015)\par
  \href{https://www.yegor256.com/2015/03/02/team-morale-myths-and-reality.html}{Team Morale: Myths and Reality} (2015)\par
}

\end{document}
