% (The MIT License)
%
% Copyright (c) 2023 Yegor Bugayenko
%
% Permission is hereby granted, free of charge, to any person obtaining a copy
% of this software and associated documentation files (the 'Software'), to deal
% in the Software without restriction, including without limitation the rights
% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
% copies of the Software, and to permit persons to whom the Software is
% furnished to do so, subject to the following conditions:
%
% The above copyright notice and this permission notice shall be included in all
% copies or substantial portions of the Software.
%
% THE SOFTWARE IS PROVIDED 'AS IS', WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
% SOFTWARE.

\documentclass{article}
\usepackage{../pmba}
\newcommand*\thetitle{Procurement Management}
\begin{document}

\plush{\pmbaTitlePage{9}}

\pmbaQuestion
  {You want to contract a \emph{new} external team of programmers, for a three-months sub-project, what type of contract is the best fit?}
  {Time-and-Material}
  {No-Money-Upfront}
  {Fixed-Fee}
  {Fake-It-Till-You-Make-It}
  {contracts}

\pmbaQuestion
  {In the middle of a project, you tell your external fixed-fee team that your in-house team will review their source code every month. The external team protests. What do you do?}
  {Cancel the contract}
  {Pay them extra}
  {Let them review your in-house code}
  {Review it, but make no comments}
  {quality}

\pmbaQuestion
  {In the middle of a contract, a freelance programmer says that the code he developed for you is his intellectual properly and you can't modify it without his permission. What can help you prove the opposite?}
  {Software license}
  {Work-for-Hire contract}
  {Telegram discussions}
  {Git history}
  {intellectual-property}

\pmbaQuestion
  {You organize a tender between a few software \emph{out-staffing} companies. What is the key \emph{metric} you should pay attention to?}
  {Dollars per hour}
  {LoC per day}
  {Bugs per release}
  {Margin per dollar}
  {tender}

\pmbaQuestion
  {What is the main reason for software outsourcing \emph{time-and-material} project failures?}
  {Cultural mismatch}
  {Leakage of talents}
  {Poor specifications}
  {Misalignment of objectives}
  {t\&m}

\pmbaQuestion
  {What is the main reason for software outsourcing \emph{fixed-fee} project failures?}
  {Cultural mismatch}
  {Leakage of talents}
  {Poor specifications}
  {Misalignment of objectives}
  {fixed}

\pmbaQuestion
  {Which open source license \emph{doesn't} allow you to use an open source software in a product that you sell?}
  {MIT}
  {GPL}
  {Apache}
  {BSD}
  {open-source}

\pmbaQuestion
  {You are planning to hire one software company out of three, organizing a tender. One company offers you a personal ``cashback,'' if you choose them. What do you do?}
  {Refuse}
  {Exclude them from the tender}
  {Ask your boss for advice}
  {Accept the money}
  {bribe}

\plush{
  \pptBanner{Homework:}
  ``A \emph{Procurement Agreement} includes terms and conditions, and may incorporate other items the the buyer specifies regarding what the seller is to perform of provide. It is the project management team's responsibility to make certain that all agreements meet the specific needs of the project while adhering to organizational procurement policies.'' --- PMBOK5

  Draft an agreement with a freelance programmer.
}

\plush{
  \pptBanner{Read this:}
  \href{https://www.yegor256.com/2015/06/15/software-outsourcing-survival-guide.html}{Software Outsourcing Survival Guide} (2015)\par
  \href{https://www.yegor256.com/2015/05/21/avoid-software-outsourcing-disaster.html}{How to Avoid a Software Outsourcing Disaster} (2015)\par
  \href{https://www.yegor256.com/2015/10/27/outsourcing-doesnt-work.html}{Why Software Outsourcing Doesn't Work ... Anymore} (2015)\par
  \href{https://www.yegor256.com/tag/outsourcing.html}{How Expensive Is Your Outsourcing Team?} (2016)\par
  \href{https://www.yegor256.com/2014/12/18/independent-technical-reviews.html}{You Do Need Independent Technical Reviews!} (2014)\par
  \href{https://www.yegor256.com/2017/11/21/trust-pay-lose.html}{Trust. Pay. Lose.} (2017)\par
}

\end{document}
