% (The MIT License)
%
% Copyright (c) 2023-2024 Yegor Bugayenko
%
% Permission is hereby granted, free of charge, to any person obtaining a copy
% of this software and associated documentation files (the 'Software'), to deal
% in the Software without restriction, including without limitation the rights
% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
% copies of the Software, and to permit persons to whom the Software is
% furnished to do so, subject to the following conditions:
%
% The above copyright notice and this permission notice shall be included in all
% copies or substantial portions of the Software.
%
% THE SOFTWARE IS PROVIDED 'AS IS', WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
% SOFTWARE.

\documentclass{article}
\usepackage{../pmba}
\newcommand*\thetitle{Integration Management}
\newcommand*\thesubtitle{}
\begin{document}

\plush{\lnTitlePage{1}{10}{kxmIPvtXKJo}}

\pmbaQuestion
  {Your team just \emph{released} a working version of a software product. The customer is \emph{happy}, but he has a few \emph{new} feature requests. As a project manager, what do you do?}
  {Implement them}
  {Ask for more money}
  {Refuse, play ``hard to get''}
  {Close the project}
  {project}

\pmbaQuestion
  {At a job interview, they ask you: ``What was the most \emph{successful} project where you were a project manager?''. What do you answer?}
  {``The one that made \$1 million to the customer''}
  {``The one that helped save people's lives''}
  {``The one where I made six-figure annual bonus''}
  {``I don't know...''}
  {success, failure, stakeholders}

\pmbaQuestion
  {You are a \emph{project manager}, a customer asks you: "Will you release a working software in three months, with all features implemented?'' You answer:}
  {``Well, I don't know...''}
  {``I believe so! We will do our best!''}
  {``Maybe, if you double the budget to cover all risks''}
  {``Yes, of course!''}
  {responsibility, observer}

\pmbaQuestion
  {Close to the \emph{end} of the project, a programmer asks you whether she will get a bonus when the project \emph{finishes} successfully. What do you answer?}
  {``I will do my best to get it for you!''}
  {``It depends on many factors''}
  {``Do you think you deserve it?''}
  {``Of course, not!''}
  {rules, charter}

\pmbaQuestion
  {If we ask four project managers ``What your project is about?'' --- which answer comes from a good PM?}
  {We are learning how to use a new technology}
  {We are building a software}
  {We are trying to develop a new algorithm}
  {We are fixing a problem}
  {objective}

\pmbaQuestion
  {The scope is unclear, the team is immature, the management is chaotic, the risks are huge, the customer doesn't know what they want. What do you do as a project manager?}
  {Find another job}
  {Set the limits of your responsibility}
  {Rely on already established mechanisms of the company}
  {Conquer!}
  {power}

\pmbaQuestion
  {A good project manager is...}
  {Leading}
  {Helping}
  {Judging}
  {Punishing}
  {rules}

\pmbaQuestion
  {What book can make you a \emph{good} project manager?}
  {``Drive'' by Daniel H. Pink, 2011}
  {``Scrum'' by Jeff Sutherland, 2014}
  {``Microsoft Project Step by Step'' by Cindy Lewis, 2019}
  {``PMP Exam Prep'' by Rita Mulcahy, 2018}
  {agile, instruments, basics}

\plush{
  \pptBanner{Homework:}\par
  ``A \emph{Project Charter} is a document issued by the project
  initiator or sponsor that formally authorizes the existence of a project,
  and provides a project manager with the authority to apply organizational
  resources to project activities.'' --- PMBOK5
}


\plush{
  \pptBanner{Read this:}\par
  \href{https://www.yegor256.com/2016/05/24/who-is-project-manager.html}{Who Is a Project Manager?} (2016)\par
  \href{https://www.yegor256.com/2016/02/18/holacracy-autocracy.html}{Holacracy or Autocracy? Both!} (2016)\par
  \href{https://www.yegor256.com/2015/06/08/deadly-sins-software-project.html}{Seven Deadly Sins of a Software Project} (2015)\par
  \href{https://www.yegor256.com/2015/09/22/micromanagement.html}{Are You a Micromanager?} (2015)\par
  \href{https://www.yegor256.com/2020/10/13/lack-of-problem.html}{Lack of Problem Is the Problem} (2020)\par
  \href{https://www.yegor256.com/2020/01/07/embrace-the-chaos.html}{Embrace the Chaos!} (2020)\par
  \href{https://www.yegor256.com/2020/12/22/self-managing-orgs.html}{Self-Managing vs. Manager-Free Organizations} (2020)\par
}

\end{document}
